---
title: "Ethos 'Essence of Research Leadership' Feedback"
subtitle: "December 2024"
#author: "Jen Beaudry"
#date: "09/12/2024"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=1.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[L]{Essence of Research Leadership} # my name in footer
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)
options(knitr.kable.NA = '')
```


```{r library, include=FALSE}
library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)
library(captioner)

# devtools::install_github("adletaw/captioner")

```

```{r functions, include=FALSE}

# use this for all tables...

styler_pdf <- function(dat) 
  dat %>%
     kableExtra::kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position", "repeat_header"))

source(here("..", "functions", "read_qualtrics.R"))
source(here("..", "functions", "meta_rename.R"))
source(here("..", "functions", "ratings_summary.R"))

table_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")

```

```{r load data, include=FALSE}

df <- here::here("data", "ethos_feedback_2024.csv") %>%
  read_qualtrics(legacy = FALSE) %>%
  filter(progress == "100") %>%  # delete those who didn't answer any questions 
  select(-c("start_date":"user_language", "sc0")) %>% 
  mutate(id = 1:n()) %>% 
  relocate (id)

# number invited to participate in the workshop
participants <- 15

```


```{r recode with metadata, include=FALSE}

# load metadata 

meta <- read_csv(here::here("data", "ethos_metadata_2024.csv"), lazy = FALSE) %>%
  filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables

# recode variable labels according to metadata

df <- meta_rename(df = df, metadata = meta, old = old_variable, new = new_variable)

```


```{r code factors, include=FALSE}


# turn all ratings variables into factors, use datapasta to do this!
# the code below works

df$expectations_met <-  factor(df$expectations_met,levels = c("Did not meet my expectations",
    "Partly met my expectations",
    "Met my expectations",
    "Exceeded my expectations"))

df$post_phd <- factor(df$post_phd, levels = c("Less than 5 years post-PhD", 
                                                  "5 to 10 years post-PhD", 
                                                  "11 to 15 years post-PhD", 
                                                  "More than 15 years post-PhD"))

# work with all rating items together because they have the same levels

cols <- c("workshop_understanding",
  "trainer_expert",
  "trainer_engaging",
  "balance",
  "work_pref_analysis",
  "content_relevance",
  "content_useful",
  "attend")

# turn the cols columns into factors
df <- df %>% 
  dplyr::mutate(across (all_of(cols), ~factor(., 
                                       levels = c("NA",
                                           "Strongly disagree",
                                           "Somewhat disagree",
                                           "Neither agree nor disagree",
                                           "Somewhat agree",
                                           "Strongly agree"))))

```


```{r captions, include = FALSE}

# I'm using this to allow me to reference the tables. 
# I'm using kable for the captions within the tables because it allows me to break 
  # the table over the pages

table_nums(name = "expectations", 
           caption = "'What did you expect from this workshop?'")

table_nums(name = "expectations_comment", 
           caption = "'Please elaborate on how the workshop aligned with your expectations.'")

table_nums(name = "career_stage", 
           caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'")

table_nums(name = "action", 
          caption = "'Did this workshop inspire you to take any immediate action(s)?'")

table_nums(name = "best_parts",
             caption = "'What were the best parts of the workshop?'")

table_nums(name = "improvement",
             caption = "'Any suggestions for improvement?'")

table_nums(name = "anything_else",
             caption = "'Anything else you want us to know?'")

fig_nums(name = "ratings_summary", 
         caption = "Ratings of different aspects of the workshop")


```

# Executive Summary

This report details the feedback from the 2024 *Essence of Research Leadership* 
workshop offered to `r participants` mid-career researchers at Flinders University. 
The program was sponsored by the Deputy Vice-Chancellor (Research) and participants
were nominated by the College Deans (Research). 

The feedback was overwhelmingly positive. Participants reported that they gained 
a greater understanding of research leadership, they appreciated the time to 
focus on their own careers and aspirations, and they are keen to incorporate 
the information into their ways of working. They also reported that they found
the opportunity to engage with researchers across the University valuable. 

I recommend continuing to offer this program on an annual basis. 


# Detailed Evaluation

Mark Douglas from Ethos designed and delivered the *Essence of Research Leadership* 
workshop. The workshop included 2 full-day sessions in June and July 2024 and a half-day 
follow-up session in September 2024. This anonymous survey was conducted 
after the second full-day session. Of the `r participants` participants who attended 
the workshop, `r nrow(df)` completed the feedback survey.

We asked participants to rate a number of items about the workshop and the trainer 
on a scale from 'strongly disagree' to 'strongly agree' (see 
`r fig_nums(name = "ratings_summary", display = "cite")`).

The ratings were very positive with most strongly agreeing that the program was 
well delivered and useful for their current and future roles. One person gave 
negative ratings (strongly disagree and somewhat disagree) 
for all items, but these negative ratings contradict their other responses, 
so I think they erroneously reversed the response scale. 

\newpage
`r fig_nums(name = "ratings_summary")`

```{r creating tibbles for all ratings, include = FALSE}

# get total n to calculate percentages

total_n <- length(df$id)

# SELECT THE RATING COLUMNS & SAVE AS A TIBBLE I WANT TO SUMMARISE & PLOT USING THE RATING_SUMMARY FUNCTION

ratings <- df %>% 
  select (c("workshop_understanding",
  "trainer_expert",
  "trainer_engaging",
  "balance",
  "work_pref_analysis",
  "content_relevance",
  "content_useful",
  "attend"))

# UPDATE THE COLUMNS PARAMETER WITH THE STRINGS FROM ABOVE

columns <- c("workshop_understanding",
  "trainer_expert",
  "trainer_engaging",
  "balance",
  "work_pref_analysis",
  "content_relevance",
  "content_useful",
  "attend")

# RUN THE FUNCTION & APPLY TO ALL COLUMNS IN OUR DF

ratings_summary <- purrr::map_dfr(columns, .f = function(column) {
	ratings_summary(ratings, column)
})

# remove the NA responses
ratings_summary <- na.omit(ratings_summary)


# also, figure out how many responded with the agree ratings. I use these in the 
  # text summaries later

```


```{r plot the ratings}

# Relevel the responses [changes order in ggplot, but not the dataframe]
# plot it first to see if I need to do this

# tor_rating$rating <- factor (rating$rating, levels = c("Strongly agree",
#                                            "Somewhat agree",
#                                            "Neither agree nor disagree",
#                                            "Somewhat disagree",
#                                            "Strongly disagree"))

# put them in reverse order of how I want them to appear
ratings_summary$rating_item <-
  factor (
    ratings_summary$rating_item,
    levels = c(
      "attend",
      "content_useful",
      "content_relevance",
      "work_pref_analysis",
      "balance",
      "trainer_engaging",
      "trainer_expert",
      "workshop_understanding"
    )
  )

# this is useful to create the plot_labs, but it doesn't need to run each time

# labs <- meta %>%
#   filter(scale == "ratings") %>%
#   pull(item_text_short) %>%
# datapasta::vector_paste_vertical()


# plot it

ggplot(ratings_summary, aes(fill = rating, y = percentage, x = rating_item)) +
  geom_bar(position="fill", stat="identity", colour = "black") +
  scale_fill_brewer(
    palette = "Blues",
    na.value = "grey50",
    direction = 1,
    labels = c(
      "N/A",
      "Strongly disagree",
      "Somewhat disagree",
      "Neither agree nor disagree",
      "Somewhat agree",
      "Strongly agree"
    )
  ) +
  labs (x = element_blank(),
        y = "Percentage") +
  theme_classic() +
theme(legend.title = element_blank()) +
    coord_flip() +
  scale_x_discrete(
    labels = c("I would attend another workshop \nfrom this trainer.", 
               "The content will be useful in my \nfuture role(s).",
               "The content was relevant to my \ncurrent role.",
                "The Work Preference Analysis \nprovided valuable insights.",
                "There was a good balance of \ngroup discussion and presentation.",
               "The trainer was engaging.",
               "The trainer is an expert in the \nsector.",
               "I gained a greater understanding of \nresearch leadership"
 )
) +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100"))

# FYI: the labels are always in opposite directions from the data set!

```


```{r expectations data, include = FALSE}

expect <- df %>% 
    dplyr::group_by (expectations_met) %>% 
  count() %>% 
    mutate (order = case_when(
         expectations_met %in% "Exceeded my expectations" ~ "1", 
         expectations_met %in% "Met my expectations" ~ "2", 
         expectations_met %in% "Partly met my expectations" ~ "3")) %>%  
  arrange (order)

```


```{r careerstage, include = FALSE}

# remove the post-PhD because it's repeated in every response
df$post_phd <- str_remove(df$post_phd, " post-PhD")

years <- df %>% 
    dplyr::group_by (post_phd) %>% 
  count() %>% 
  mutate (order = case_when(
          post_phd == "Less than 5 years" ~ "1", 
          post_phd == "5 to 10 years" ~ "2", 
          post_phd == "11 to 15 years" ~ "3", 
          post_phd == "More than 15 years" ~ "4")) %>% 
  arrange (order)

# change the text to be used in the markdown
years$post_phd <- str_replace(years$post_phd, "Less", "less")
years$post_phd <- str_replace(years$post_phd, "More", "more")

```

\

As indicated in `r table_nums("expectations", display = "cite")`, the respondents
had a good understanding of what they could expect from the workshop. 


```{r expectations table, include = TRUE}

expectations <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expectations) %>% 
  filter (!is.na(expectations))


kable(
  expectations,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What did you expect from this workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```

\newpage
With these expectations in mind, respondents indicated whether the program aligned with their expectations. 
Of the `r nrow(df)` respondents, 

  * `r round((expect[1,2]/nrow(df))*100,2)`% said that it exceeded their expectations, 
  * `r round((expect[2,2]/nrow(df))*100,2)`% said that it met their expectations, 
  * `r round((expect[3,2]/nrow(df))*100,2)`% said that it partly met their expectations, and 
  * no one indicated that it did not meet their expectations. 

Their explanations of how the program aligned with their expectations are shown 
in `r table_nums("expectations_comment", display = "cite")`. 


```{r expectations elaboration table, include = TRUE}

expectations_comment <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, expectations_comment) %>% 
  filter (!is.na(expectations_comment))


kable(
  expectations_comment,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on how the workshop aligned with your expectations.'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```

We had a mix of participants in this workshop (nominated by their Deans of Research). 
The respondents to the survey reflected this mix; 
`r years[1,2]` respondent was `r years [1,1]` post-PhD, 
`r years[2,2]` respondents were `r years [2,1]` post-PhD,
`r years[3,2]` respondents were `r years [3,1]` post-PhD, and 
`r years[4,2]` respondents were `r years [4,1]` post-PhD. 

Participants reported whether or not the program aligned with their career 
stage and explained why or why not it was suited to them (see `r table_nums("career_stage", display = "cite")`).
Despite the range of participants' career stages, all respondents indicated that the
program was appropriate for their career stage. 


```{r career_stage table, include = TRUE}

career_stage <- df %>% 
  select(c(id, post_phd, career_stage_yes, career_stage_no)) %>% 
  replace_na(list(careerstage_yes = "", careerstage_no = "")) %>% 
  arrange(desc(post_phd))


kable(
  career_stage,
  longtable = T,
  booktabs = T, 
  align = c('clll'),
  linesep = "\\addlinespace",
  caption = "'Please elaborate on whether this workshop was appropriate for your career stage.'",
  col.names = c("Respondent", "Years post PhD", "Reasons why it was appropriate", "Reasons why it was not appropriate")
  ) %>%
  column_spec (column = 3, width = "5cm") %>%
   column_spec (column = 4, width = "5cm") %>%
    styler_pdf

```


As shown in `r table_nums("action", display = "cite")`, respondents were inspired
by the program to take a variety of actions ranging from sharing the information 
they learned with others, to planning their career, to working on their research 
pitch.

```{r action table, include = TRUE}

action <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, actions) %>% 
  filter (!is.na(actions))


kable(
  action,
  booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Did this workshop inspire you to take any immediate action(s)?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
  styler_pdf

```

The best parts of the workshop included interacting with other colleagues across 
the University, having focused time to reflect on their careers, and learning more
about university governance (see `r table_nums("best_parts", display = "cite")`).


```{r best_parts table, include = TRUE}

best <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, best_parts) %>% 
  filter (!is.na(best_parts))

kable(
  best,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'What were the best parts of the workshop?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
    styler_pdf
```

Not surprisingly given the positive feedback, participants had few suggestions 
as to how the program could be improved (see `r table_nums("improvement", display = "cite")`).


```{r improvement table, include = TRUE}

improve <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, improvement) %>% 
  filter (!is.na(improvement))


kable(
  improve,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Any suggestions for improvement?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
   styler_pdf

```

Finally, we asked the participants if there was anything else they wanted us to know
(see `r table_nums("anything_else", display = "cite")`).



```{r anything else table, include = TRUE}

anything_else <- df %>% 
    mutate(Participant = 1:n()) %>% 
  select (Participant, anything_else) %>% 
  filter (!is.na(anything_else))


kable(
  anything_else,
    booktabs = T, 
  align = c('cl'),
  linesep = "\\addlinespace",
  caption = "'Anything else you want us to know?'",
  col.names = c("Respondent", "Response")
  ) %>%
  column_spec (column = 2, width = "14cm") %>%
    styler_pdf


```

\

If you have any questions about this report or the program, please contact 
Dr Jen Beaudry, Manager, Researcher Training, Development and Communication 
in Research Development and Support. 
